---
title: "Dashboard"
author: "Angelo Werleman"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    code_folding: show
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(ggcorrplot)
library(cowplot)
source("compmus.R")
```

```{r}
#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(5.0, 2.0, 3.5, 2.0, 4.5, 4.0, 2.0, 4.5, 2.0, 3.5, 1.5, 4.0)
minor_key <-
  c(5.0, 2.0, 3.5, 4.5, 2.0, 4.0, 2.0, 4.5, 3.5, 2.0, 1.5, 4.0)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )
```

### Chordogram {.storyboard}

```{r}
chordogram_plot <- "features/elze-s-1.json" |> 
  compmus_chroma(norm = "identity") |> 
  compmus_match_pitch_templates(
    chord_templates,         # Change to chord_templates if desired
    norm = "identity",       # Try different norms (and match it with what you used in `compmus_chroma`)
    distance = "cosine"   # Try different distance metrics
  ) |>
  ggplot(aes(x = time, y = name, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = "Template", fill = NULL) +
  theme_classic() 

  chordogram_plot
```

---------------

I am still waiting for the corpus to be updated with the music I submitted, so for this assignment, I will continue using Elze’s track (Elze_s_1) as my reference.

I've come to realize how much genre can affect a chordogram or really, any kind of spectral visualization. Since this is a grunge/alternative band, their use of heavy distortion introduces rich overtones and harmonics, making it harder to clearly distinguish between chords or even the key. The added harmonic content from distortion can blur the lines between different tonal centers, making chord recognition less precise.

### Keygram {.storyboard}

```{r}
keygram_plot <- "features/elze-s-1.json" |> 
  compmus_chroma(norm = "identity") |> 
  compmus_match_pitch_templates(
    key_templates,         # Change to chord_templates if desired
    norm = "identity",       # Try different norms (and match it with what you used in `compmus_chroma`)
    distance = "cosine"   # Try different distance metrics
  ) |>
  ggplot(aes(x = time, y = name, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = "Template", fill = NULL) +
  theme_classic()

  keygram_plot
```

---------------

In this keygram, it seems to do a worse job at identifying the key, especially in this genre. The smooth variations in the keygram make it less visible when dealing with louder, more distorted, or droning music, all of which are defining characteristics of grunge. The heavy use of distortion and overtones likely introduces inconsistencies in key detection, resulting in a more blurred representation.

In contrast, the chromagram appears to be more effective at visualizing the key. As seen in the next section, I will place them side by side to highlight these differences.

### Combined {.storyboard}

```{r}
chromagram_plot <- "features/elze-s-1.json" |>                           # Change the track
  compmus_chroma(norm = "identity") |>                 # Change the norm
  ggplot(aes(x = time, y = pc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:11,
    minor_breaks = NULL,
    labels = c(
                "C", "C#|Db", "D", "D#|Eb",
                "E", "F", "F#|Gb", "G",
                "G#|Ab", "A", "A#|Bb", "B"
              )
  ) +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()                                      # Change the theme?

plot_grid(keygram_plot, chromagram_plot, ncol = 2)
```

------------

Overall, the challenges in key detection for grunge music stem from the genre’s heavy use of distortion, power chords, and tonal ambiguity. The extra overtones introduced by distortion create harmonics that confuse key detection algorithms, leading to instability in the keygram. Additionally, since power chords lack a clear major or minor identity, keygrams, which rely on full triads, struggle to establish a consistent key, causing fluctuations in the results. Lastly, the smoothing effect of keygrams further reduces their reliability in a genre where harmonic transitions are often blurred or undefined. In contrast, the chromagram proves to be a more effective tool for visualizing tonal centers, as it captures the raw pitch-class data without forcing a rigid key interpretation. This makes it a better choice for analyzing grunge and other heavily distorted music styles.

### Chromagram {.storyboard}

```{r}
chromagram_plot <- "features/elze-s-1.json" |>                           # Change the track
  compmus_chroma(norm = "identity") |>                 # Change the norm
  ggplot(aes(x = time, y = pc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:11,
    minor_breaks = NULL,
    labels = c(
                "C", "C#|Db", "D", "D#|Eb",
                "E", "F", "F#|Gb", "G",
                "G#|Ab", "A", "A#|Bb", "B"
              )
  ) +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()                                      # Change the theme?
  
  chromagram_plot

```

------------------------------------------------------------------------

Unfortunately, just like last week, my music is still not in the class corpus, so I decided to analyze the track Elze_s_1 instead. While discussing the track with Elze, she informed me that it’s from her band, which plays alternative rock/grunge. This genre choice offers an interesting and distinct sonic palette, and through this analysis, I’ll explore the song’s harmonic and timbral elements to uncover how its structure is defined in music like alternative rock/grunge, starting with the chromagram to reveal the key it’s in.

The chromagram highlights the notes B♭ - C - D♭ - E♭ - F - G♭ - A♭ - (B♭), which corresponds to the B-flat minor scale. This suggests that the track is primarily in the key of B-flat minor, reinforcing a darker, more melancholic tonality.

### Chroma-based self-similarity {.storyboard}

```{r}
"features/elze-s-1.json" |>                           # Change the track
  compmus_chroma(norm = "identity") |>                 # Change the norm
  compmus_self_similarity(
    feature = pc,
    distance = "euclidean"                             # Change the distance
  ) |>   
  ggplot(aes(x = xtime, y = ytime, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()                                      # Change the theme?
```

------------------------------------------------------------------------

The chroma-based similarity matrix displays thick yellow diagonal lines, indicating strong harmonic repetition. However, I can’t find a clear correlation between these lines and the actual song structure. This suggests that while harmonic content may be repeating, it doesn’t align obviously with the perceived sections of the track. This could be due to subtle chord variations, modal ambiguity, or the prominence of timbral changes in defining the song’s form, which is common in alternative rock/grunge.

### Timbre-based self-similarity {.storyboard}

```{r}
"features/elze-s-1.json" |>                           # Change the track
  compmus_mfccs(norm = "identity") |>                  # Change the norm
  compmus_self_similarity(
    feature = mfcc,
    distance = "euclidean"                             # Change the distance
  ) |>
  ggplot(aes(x = xtime, y = ytime, fill = d)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()                                      # Change the theme?
```

------------------------------------------------------------------------

The timbre-based similarity matrix reveals structure more clearly than the chroma-based matrix, suggesting that textural changes drive the song’s form, which is common in alternative rock/grunge. Key moments include 8s, where the drums enter, and 26s, where the guitar fades and the drums become more relaxed for the verse. The chroma matrix shows less variation, indicating that harmony remains stable while instrumentation and mix shape the song’s sections. This highlights the role of timbre in defining musical form, especially in grunge and alt-rock, where dynamic shifts and raw textures are essential.

### Introduction {.storyboard}

Unfortunately, due to uploading my files to the comment section of the first homework assignment, my songs did not appear in the class corpus. I attempted to run my tracks through Essentia using Python, but encountered installation errors. Therefore, for this assignment, I will focus on comparing the class corpus with the AI Song Contest (AISC) dataset.

My mini research will focus on identifying the outliers in both datasets, particularly in the feature of danceability, while also considering potential factors such as tempo and instrumentalness. I will begin by analyzing these outliers based on the perceived values of these features, without listening to the tracks. After identifying the outliers, I will then listen to the tracks and compare my subjective interpretation of these features to the results from Essentia. This process will allow me to explore how well the feature extraction methods align with my own musical perceptions and whether the outliers identified by Essentia fit within a broader musical context.

### Visualizing the Class Corpus {.tabset .storyboard}

```{r}
compmus2025 <- read_csv("compmus2025.csv")

compmus2025 |>                   # Start with the data
    ggplot(                     # Set up the plot.
        aes(
            x = tempo,
            y = danceability,
            size = arousal,
            colour = instrumentalness,
            label = artist
        )
    ) +
    geom_point() +              # Scatter plot.
    geom_rug(linewidth = 0.1) + 
  
    scale_x_continuous(         # Fine-tune the x axis.
        limits = c(50, 180),
        breaks = c(50, 100, 150, 200), # Specify grid lines
        minor_breaks = NULL       # Remove 'minor' grid lines.
    ) +
    scale_y_continuous(         # Fine-tune the y axis in the same way.
        limits = c(0, 1),
        breaks = c(1, 5, 9),
        minor_breaks = NULL
    ) +
    scale_colour_viridis_c() +  # Use the popular viridis colour palette.
    scale_size_continuous(      # Fine-tune the sizes of each point.
        trans = "exp",            # Use an exp transformation to emphasise loud..
        guide = "none"            # Remove the legend for size.
    ) +
    theme_minimal() +             # Use a simpler theme.
    labs(                       # Make the titles nice.
        x = "Tempo",
        y = "Danceability",
        colour = "Instrumentalness"
    )
ggplotly()
```

------------------------------------------------------------------------

This scatter plot visualizes the **Class Corpus** dataset, focusing on the relationship between **tempo** (x-axis) and **danceability** (y-axis), with **instrumentalness** represented by color.

### Visualizing the AI Song contest

```{r}
aisc2024 <- read_csv("aisc2024.csv")

aisc2024 |>                   # Start with the data
    ggplot(                     # Set up the plot.
        aes(
            x = tempo,
            y = danceability,
            size = arousal,
            colour = instrumentalness,
            label = artist
        )
    ) +
    geom_point() +              # Scatter plot.
    geom_rug(linewidth = 0.1) + 
  scale_x_continuous(         # Fine-tune the x axis.
        limits = c(50, 180),
        breaks = c(50, 100, 150, 200), # Specify grid lines
        minor_breaks = NULL       # Remove 'minor' grid lines.
    ) +
    scale_y_continuous(         # Fine-tune the y axis in the same way.
        limits = c(0, 1),
        breaks = c(1, 5, 9),
        minor_breaks = NULL
    ) +
    scale_colour_viridis_c() +  # Use the popular viridis colour palette.
    scale_size_continuous(      # Fine-tune the sizes of each point.
        trans = "exp",            # Use an exp transformation to emphasise loud..
        guide = "none"            # Remove the legend for size.
    ) +
    theme_minimal() +             # Use a simpler theme.
    labs(                       # Make the titles nice.
        x = "Tempo",
        y = "Danceability",
        colour = "Instrumentalness"
    )
ggplotly()
```

------------------------------------------------------------------------

This scatter plot visualizes the **AI Song Contest** 2024 dataset, displaying the relationship between **tempo** (x-axis) and **danceability** (y-axis), with **instrumentalness** represented by color.

### Exploring Danceability Across Datasets {.storyboard}

```{r}
compmus2025 <- read_csv("compmus2025.csv")
aisc2024 <- read_csv("aisc2024.csv")

compmus2025$dataset <- "compmus2025"
aisc2024$dataset <- "aisc2024"

# Combine the datasets
combined_data <- bind_rows(compmus2025, aisc2024)

ggplot(combined_data, aes(x = tempo, 
                          y = danceability,
                  color = instrumentalness,
                          label = artist, shape = dataset)) +
    geom_point(alpha = 0.6) +
  scale_colour_viridis_c() +
   theme_minimal() +
    labs(title = "Tempo vs Danceability",
         x = "Tempo",
         y = "Danceability")
ggplotly()
```

------------------------------------------------------------------------

```{r, echo=TRUE}
find_outliers <- function(data, feature_name) {
  lowest_value <- min(data[[feature_name]], na.rm = TRUE)
  highest_value <- max(data[[feature_name]], na.rm = TRUE)
  lowest_song <- data %>% filter(!!sym(feature_name) == lowest_value) %>% pull(artist)
  highest_song <- data %>% filter(!!sym(feature_name) == highest_value) %>% pull(artist)
  
  return(list(lowest_value = lowest_value, highest_value = highest_value,
              lowest_song = lowest_song, highest_song = highest_song))
}

compmus_tempo <- find_outliers(compmus2025, "tempo")
compmus_dance <- find_outliers(compmus2025, "danceability")
compmus_instr <- find_outliers(compmus2025, "instrumentalness")

aisc_tempo <- find_outliers(aisc2024, "tempo")
aisc_dance <- find_outliers(aisc2024, "danceability")
aisc_instr <- find_outliers(aisc2024, "instrumentalness")

```

**Identified Outliers in Both Datasets**

**Class Corpus (compmus2025):**

Least danceable track: `r compmus_dance$lowest_song`

Tempo: **`r compmus_tempo$lowest_value`** BPM

Instrumentalness: **`r compmus_instr$lowest_value`**

**Most danceable track**: `r compmus_dance$highest_song`

Tempo: **`r compmus_tempo$highest_value`** BPM

Instrumentalness: **`r compmus_instr$highest_value`**

AI Song Contest Dataset (aisc2024):

**Least danceable track**: `r aisc_dance$lowest_song`

Tempo: **`r aisc_tempo$lowest_value`** BPM

Instrumentalness: **`r aisc_instr$lowest_value`**

**Most danceable track**: `r aisc_dance$highest_song`

Tempo: **`r aisc_tempo$highest_value`** BPM

Instrumentalness: **`r aisc_instr$highest_value`**

### Conclusion & Discussion {.storyboard}

The relationship between tempo, **instrumentalness**, and **danceability** in these tracks reveals some interesting patterns. **The least danceable** track from the class corpus, "erik-l-1," stands out with its slow tempo (30 BPM) and relatively low **instrumentalness** (**0.1309513**). While the track may lack the vocal presence typically associated with more energetic dance tracks, its **low** **instrumentalness** and slow tempo make it feel more like a classical piece, which could be associated with more reserved forms of dancing, like a waltz. While not traditionally considered "danceable," its rhythm could still engage listeners in a more contemplative, slower-moving way.

"Roemer-i-1," **the most danceable** track in the class corpus, shows how the combination of a **fast tempo** (**176 BPM**) and **high** **instrumentalness** (**0.9554076**) can elevate a track’s energy. Its beat, which I would categorize as IDM or trip-hop, contributes to its overall danceability. The high tempo paired with intricate percussion and experimental elements makes this track ideal for a more eclectic and energetic dance environment.

In the AI Song Contest dataset, "Vonpsyche" stands out with its **low danceability**, which I think can be explained by its **moderate** **tempo** (**63** **BPM**) and **moderate** **instrumentalness** (**0.3695597**). The track, mostly made up of spoken word over an ambient beat, prioritizes atmosphere over rhythm, making it harder to categorize as a dance track. Its focus on vocal delivery and mood over a driving beat directly impacts its lower danceability score.

Finally, "Almost Human" is **the most danceable** track in the AI Song Contest dataset. With its tempo of **155** **BPM** and **high** **instrumentalness** (**0.9040143**), this track showcases the power of electronic dance music. Its four-on-the-floor beat and deep, rhythmic structure make it highly danceable, with its instrumental complexity adding a layer of richness that keeps the energy flowing throughout.

It is also important to remember that the analysis here is based on an excerpt of only four tunes from the class corpus. While this provides valuable insights, it’s a small sample size and may not fully represent the overall dataset. However, despite the limited sample, Essentia did a good job in identifying key features that align with both subjective interpretations and musical expectations, suggesting that the tool can be a useful starting point for analyzing larger datasets.
